### 2013-07-22 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
working on frontmatter

In this chapter the fundamentals of Newton's method will be presented
along with a brief discussion of inexact Newton methods. Newton-Krylov
methods, a variant of inexact Newton methods, will be outlined along
with two common techniques for Jacobian generation as a means of
defining current practices. Following this, the new algorithm will be
presented and implementation details will be discussed. Using the new
algorithm and a production fluid physics code, a group of challenging
nonlinear benchmark problems for the Navier-Stokes equations will be
used to verify the correctness of the method relative to solutions
obtained using conventional methods in various flow regimes. Finally,
we will compare the performance of the new method against contemporary
Newton-Krylov methods for the same benchmark problems.

@@

\subsubsection{Backward-Facing Step Problem}
\label{subsubsec:backward_facing_step}
The third benchmark was generated by Gartling in 1990 and consists of
both flow over a backward step and an outflow boundary condition
\citep{gartling_test_1990}. Using the mass and momentum equations
while neglecting the energy equation, this problem utilizes a longer
domain with a 1/25 aspect ratio used for this work\footnote{The
  literature on this benchmark suggests using a domain with a 1/30
  aspect ratio to reduce the effect of the outflow boundary condition
  on the upstream recirculation zones. Using a 1/25 aspect ratio for
  this work was not observed to disturb the recirculation zones and
  was therefore used to reduce memory pressure on the FANM solver.}
with the boundary conditions as shown in
Figure~\ref{fig:backward_facing_step}. For this work, a slightly
different parabolic formulation was used than in the benchmark. In the
benchmark solutions, the average velocity in the parabola was 2/3 that
of the maximum velocity while formula given in
Figure~\ref{fig:backward_facing_step} produces a more plug-like flow
with an average velocity of 3/4 that of the maximum velocity.

@@

In this problem, the inflow condition is specified by a fully-formed
parabolic flow profile over a zero velocity boundary representing a
step. The flow over this step will generate a recirculating backflow
under the inlet flow towards the step and at higher Reynolds numbers a
recirculating zone will form farther downstream from the step. As in
the lid driven cavity problem, the nonlinear behavior of this
benchmark and the difficulty in obtaining a solution is dictated by
the Reynolds number of the fluid. In Shadid's work, a Reynolds numbers
up to 800 were used.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -1.288835730E-05 & -1.288835730E-05 \\
      Minimum $U_x$ & -3.677243960E+00 & -3.677243960E+00 \\
      Maximum $U_x$ & 3.688908550E+00 & 3.688908550E+00 \\
      \hline
      Average $U_y$ & 3.403670530E-02 & 3.403670530E-02 \\
      Minimum $U_y$ & -3.721178580E+00 & -3.721178580E+00 \\
      Maximum $U_y$ & 3.791483420E+00 & 3.791483420E+00 \\
      \hline
      Average $P$ & 2.345554770E+02 & 2.345554770E+02 \\
      Minimum $P$ & -5.509779180E+00 & -5.509779180E+00 \\
      Maximum $P$ & 4.994885560E+02 & 4.994885560E+02 \\
      \hline
      Average $T$ & 3.595148700E-02 & 3.595148700E-02 \\
      Minimum $T$ & 2.092448340E-04 & 2.092448340E-04 \\
      Maximum $T$ & 7.178874510E-02 & 7.178874510E-02 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{3}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e3_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -7.489201240E-04 & -7.489201240E-04 \\
      Minimum $U_x$ & -1.607318000E+01 & -1.607318000E+01 \\
      Maximum $U_x$ & 1.669098270E+01 & 1.669098270E+01 \\
      \hline
      Average $U_y$ & 3.377624420E-01 & 3.377624420E-01 \\
      Minimum $U_y$ & -1.932174800E+01 & -1.932174800E+01 \\
      Maximum $U_y$ & 2.047326820E+01 & 2.047326820E+01 \\
      \hline
      Average $P$ & 1.861894950E+03 & 1.861894950E+03 \\
      Minimum $P$ & -3.353416240E+01 & -3.353416240E+01 \\
      Maximum $P$ & 4.440642810E+03 & 4.440642810E+03 \\
      \hline
      Average $T$ & 3.510568440E-01 & 3.510568440E-01 \\
      Minimum $T$ & 2.092448340E-04 & 2.092448340E-04 \\
      Maximum $T$ & 7.178874510E-02 & 7.178874510E-02 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{4}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e4_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -2.043639370E-02 & -2.043639370E-02 \\
      Minimum $U_x$ & -3.814922470E+01 & -3.814922470E+01 \\
      Maximum $U_x$ & -3.814922470E+01 & -3.814922470E+01 \\
      \hline
      Average $U_y$ & 2.774864300E+00 & 2.774864300E+00 \\
      Minimum $U_y$ & -6.038682990E+01 & -6.038682990E+01 \\
      Maximum $U_y$ & 7.873873560E+01 & 7.873873560E+01 \\
      \hline
      Average $P$ & 1.324208380E+04 & 1.324208380E+04 \\
      Minimum $P$ & -1.390235490E+02 & -1.390235490E+02 \\
      Maximum $P$ & 3.559215530E+04 & 3.559215530E+04 \\
      \hline
      Average $T$ & 3.027827770E+00 & 3.027827770E+00 \\
      Minimum $T$ & 1.626405740E-02 & 1.626405740E-02 \\
      Maximum $T$ & 7.162571130E+00 & 7.162571130E+00 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{5}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e5_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & -1.802569840E-01 & -1.802569840E-01 \\
      Minimum $U_x$ & -6.292084130E+01 & -6.292084130E+01 \\
      Maximum $U_x$ & 2.951113240E+02 & 2.951113240E+02 \\
      \hline
      Average $U_y$ & 1.336398550E+01 & 1.336398550E+01 \\
      Minimum $U_y$ & -1.345663290E+02 & -1.345663290E+02 \\
      Maximum $U_y$ & 3.227873890E+02 & 3.227873890E+02 \\
      \hline
      Average $P$ & 6.354313840E+04 & 6.354313840E+04 \\
      Minimum $P$ & -1.356309630E+02 & -1.356309630E+02 \\
      Maximum $P$ & 2.316308730E+05 & 2.316308730E+05 \\
      \hline
      Average $T$ & 1.780727610E+01 & 1.780727610E+01 \\
      Minimum $T$ & 8.265788890E-02 & 8.265788890E-02 \\
      Maximum $T$ & 7.098873170E+01 & 7.098873170E+01 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{6}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e6_results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 1.165632320E-01 & 1.165632320E-01 \\
      Minimum $U_x$ & -2.423642920E+01 & -2.423642920E+01 \\
      Maximum $U_x$ & 9.742670880E+01 & 9.742670880E+01 \\
      \hline
      Average $U_y$ & 2.038480420E-02 & 2.038480420E-02 \\
      Minimum $U_y$ & -5.266315430E+01 & -5.266315430E+01 \\
      Maximum $U_y$ & 2.720044160E+01 & 2.720044160E+01 \\
      \hline
      Average $P$ & -1.656193900E+02 & -1.656193900E+02 \\
      Minimum $P$ & -9.635479370E+03 & -9.635479370E+03 \\
      Maximum $P$ & 1.854517020E+04 & 1.854517020E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 100.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re100_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 3.382078040E-01 & 3.382078040E-01 \\
      Minimum $U_x$ & -9.467140360E+01 & -9.467140360E+01 \\
      Maximum $U_x$ & 2.895885380E+02 & 2.895885380E+02 \\
      \hline
      Average $U_y$ & 8.780242440E-02 & 8.780242440E-02 \\
      Minimum $U_y$ & -1.830156060E+02 & -1.830156060E+02 \\
      Maximum $U_y$ & 8.827373340E+01 & 8.827373340E+01 \\
      \hline
      Average $P$ & -2.830380160E+03 & -2.830380160E+03 \\
      Minimum $P$ & -2.352177540E+04 & -2.352177540E+04 \\
      Maximum $P$ & 9.254997120E+04 & 9.254997120E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 300.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 5.098921320E-01 & 5.098921320E-01 \\
      Minimum $U_x$ & -1.731861690E+02 & -1.731861690E+02 \\
      Maximum $U_x$ & 4.789146040E+02 & 4.789146040E+02 \\
      \hline
      Average $U_y$ & 1.365493140E-01 & 1.365493140E-01 \\
      Minimum $U_y$ & -3.170930360E+02 & -3.170930360E+02 \\
      Maximum $U_y$ & 1.655401440E+02 & 1.655401440E+02 \\
      \hline
      Average $P$ & -9.378317550E+03 & -9.378317550E+03 \\
      Minimum $P$ & -4.155215280E+04 & -4.155215280E+04 \\
      Maximum $P$ & 2.058742010E+05 & 2.058742010E+05 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 500.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re500_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & 6.479541170E-01 & 6.479541170E-01 \\
      Minimum $U_x$ & -2.550685400E+02 & -2.550685400E+02 \\
      Maximum $U_x$ & 6.663054900E+02 & 6.663054900E+02 \\
      \hline
      Average $U_y$ & 1.833690840E-01 & 1.833690840E-01 \\
      Minimum $U_y$ & -4.491052980E+02 & -4.491052980E+02 \\
      Maximum $U_y$ & 2.474376340E+02 & 2.474376340E+02 \\
      \hline
      Average $P$ & 1.833690840E-01 & 1.833690840E-01 \\
      Minimum $P$ & -6.241704500E+04 & -6.241704500E+04 \\
      Maximum $P$ & 3.518174810E+05 & 3.518174810E+05 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 700.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re700_results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\ 
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\ 
      Maximum $U_y$ & \\ 
      \hline
      Average $P$ & \\ 
      Minimum $P$ & \\ 
      Maximum $P$ & \\ 
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 200.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re200_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\
      Maximum $U_y$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 300.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\
      Maximum $U_y$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 400.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re400_results}
\end{table}

>>>>

In this chapter the fundamentals of Newton's method will be presented
along with a brief discussion of inexact Newton methods. Newton-Krylov
methods, a variant of inexact Newton methods, will be outlined
including with two common techniques for numerically representing the
Jacobian most commonly used in today's applications. Following this,
the new algorithm will be presented and implementation details will be
discussed. Using the new algorithm and a production fluid physics
code, a group of challenging nonlinear benchmark problems for the
Navier-Stokes equations will be used to verify the correctness of the
method relative to solutions obtained using conventional methods in
various flow regimes and geometries. Finally, we will compare the
performance of the new method against contemporary Newton-Krylov
methods for the same benchmark problems.

@@

\subsubsection{Backward-Facing Step Problem}
\label{subsubsec:backward_facing_step}
The third benchmark was generated by Gartling in 1990 and consists of
both flow over a backward step and an outflow boundary condition
\citep{gartling_test_1990}. Using the mass and momentum equations
while neglecting the energy equation, this problem utilizes a longer
domain with a 1/25 aspect ratio used for this work\footnote{The
  literature on this benchmark suggests using a domain with a 1/30
  aspect ratio to reduce the effect of the outflow boundary condition
  on the upstream recirculation zones. Using a 1/25 aspect ratio for
  this work was not observed to disturb the recirculation zones and
  was therefore used to reduce memory pressure on the FANM solver.}
with the boundary conditions as shown in
Figure~\ref{fig:backward_facing_step}.

@@

In this problem, the inflow condition is specified by a fully-formed
parabolic flow profile over a zero velocity boundary representing a
step. For this work, a slightly different parabolic formulation for
the inlet velocities was used than in the benchmark. In the benchmark
solutions, the average velocity in the parabola was 2/3 that of the
maximum velocity while the formula given in
Figure~\ref{fig:backward_facing_step} produces a more plug-like flow
with an average velocity 3/4 that of the maximum velocity. The flow
over this step will generate a recirculating backflow under the inlet
flow towards the step and at higher Reynolds numbers a recirculating
zone will form farther downstream from the step. As in the lid driven
cavity problem, the nonlinear behavior of this benchmark and the
difficulty in obtaining a solution is dictated by the Reynolds number
of the fluid. In Shadid's work, a Reynolds numbers up to 800 were
used.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & -1.288835730E-05 & -1.288835730E-05 \\
      Minimum $U$ & -3.677243960E+00 & -3.677243960E+00 \\
      Maximum $U$ & 3.688908550E+00 & 3.688908550E+00 \\
      \hline
      Average $V$ & 3.403670530E-02 & 3.403670530E-02 \\
      Minimum $V$ & -3.721178580E+00 & -3.721178580E+00 \\
      Maximum $V$ & 3.791483420E+00 & 3.791483420E+00 \\
      \hline
      Average $P$ & 2.345554770E+02 & 2.345554770E+02 \\
      Minimum $P$ & -5.509779180E+00 & -5.509779180E+00 \\
      Maximum $P$ & 4.994885560E+02 & 4.994885560E+02 \\
      \hline
      Average $T$ & 3.595148700E-02 & 3.595148700E-02 \\
      Minimum $T$ & 2.092448340E-04 & 2.092448340E-04 \\
      Maximum $T$ & 7.178874510E-02 & 7.178874510E-02 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{3}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e3_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & -7.489201240E-04 & -7.489201240E-04 \\
      Minimum $U$ & -1.607318000E+01 & -1.607318000E+01 \\
      Maximum $U$ & 1.669098270E+01 & 1.669098270E+01 \\
      \hline
      Average $V$ & 3.377624420E-01 & 3.377624420E-01 \\
      Minimum $V$ & -1.932174800E+01 & -1.932174800E+01 \\
      Maximum $V$ & 2.047326820E+01 & 2.047326820E+01 \\
      \hline
      Average $P$ & 1.861894950E+03 & 1.861894950E+03 \\
      Minimum $P$ & -3.353416240E+01 & -3.353416240E+01 \\
      Maximum $P$ & 4.440642810E+03 & 4.440642810E+03 \\
      \hline
      Average $T$ & 3.510568440E-01 & 3.510568440E-01 \\
      Minimum $T$ & 2.092448340E-04 & 2.092448340E-04 \\
      Maximum $T$ & 7.178874510E-02 & 7.178874510E-02 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{4}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e4_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & -2.043639370E-02 & -2.043639370E-02 \\
      Minimum $U$ & -3.814922470E+01 & -3.814922470E+01 \\
      Maximum $U$ & -3.814922470E+01 & -3.814922470E+01 \\
      \hline
      Average $V$ & 2.774864300E+00 & 2.774864300E+00 \\
      Minimum $V$ & -6.038682990E+01 & -6.038682990E+01 \\
      Maximum $V$ & 7.873873560E+01 & 7.873873560E+01 \\
      \hline
      Average $P$ & 1.324208380E+04 & 1.324208380E+04 \\
      Minimum $P$ & -1.390235490E+02 & -1.390235490E+02 \\
      Maximum $P$ & 3.559215530E+04 & 3.559215530E+04 \\
      \hline
      Average $T$ & 3.027827770E+00 & 3.027827770E+00 \\
      Minimum $T$ & 1.626405740E-02 & 1.626405740E-02 \\
      Maximum $T$ & 7.162571130E+00 & 7.162571130E+00 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{5}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e5_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & -1.802569840E-01 & -1.802569840E-01 \\
      Minimum $U$ & -6.292084130E+01 & -6.292084130E+01 \\
      Maximum $U$ & 2.951113240E+02 & 2.951113240E+02 \\
      \hline
      Average $V$ & 1.336398550E+01 & 1.336398550E+01 \\
      Minimum $V$ & -1.345663290E+02 & -1.345663290E+02 \\
      Maximum $V$ & 3.227873890E+02 & 3.227873890E+02 \\
      \hline
      Average $P$ & 6.354313840E+04 & 6.354313840E+04 \\
      Minimum $P$ & -1.356309630E+02 & -1.356309630E+02 \\
      Maximum $P$ & 2.316308730E+05 & 2.316308730E+05 \\
      \hline
      Average $T$ & 1.780727610E+01 & 1.780727610E+01 \\
      Minimum $T$ & 8.265788890E-02 & 8.265788890E-02 \\
      Maximum $T$ & 7.098873170E+01 & 7.098873170E+01 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity FANM verification for a
      Rayleigh number of \sn{1}{6}.} \textit{The values reported are
      global minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:convection_ra1e6_results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 1.165632320E-01 & 1.165632320E-01 \\
      Minimum $U$ & -2.423642920E+01 & -2.423642920E+01 \\
      Maximum $U$ & 9.742670880E+01 & 9.742670880E+01 \\
      \hline
      Average $V$ & 2.038480420E-02 & 2.038480420E-02 \\
      Minimum $V$ & -5.266315430E+01 & -5.266315430E+01 \\
      Maximum $V$ & 2.720044160E+01 & 2.720044160E+01 \\
      \hline
      Average $P$ & -1.656193900E+02 & -1.656193900E+02 \\
      Minimum $P$ & -9.635479370E+03 & -9.635479370E+03 \\
      Maximum $P$ & 1.854517020E+04 & 1.854517020E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 100.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re100_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 3.382078040E-01 & 3.382078040E-01 \\
      Minimum $U$ & -9.467140360E+01 & -9.467140360E+01 \\
      Maximum $U$ & 2.895885380E+02 & 2.895885380E+02 \\
      \hline
      Average $V$ & 8.780242440E-02 & 8.780242440E-02 \\
      Minimum $V$ & -1.830156060E+02 & -1.830156060E+02 \\
      Maximum $V$ & 8.827373340E+01 & 8.827373340E+01 \\
      \hline
      Average $P$ & -2.830380160E+03 & -2.830380160E+03 \\
      Minimum $P$ & -2.352177540E+04 & -2.352177540E+04 \\
      Maximum $P$ & 9.254997120E+04 & 9.254997120E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 300.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 5.098921320E-01 & 5.098921320E-01 \\
      Minimum $U$ & -1.731861690E+02 & -1.731861690E+02 \\
      Maximum $U$ & 4.789146040E+02 & 4.789146040E+02 \\
      \hline
      Average $V$ & 1.365493140E-01 & 1.365493140E-01 \\
      Minimum $V$ & -3.170930360E+02 & -3.170930360E+02 \\
      Maximum $V$ & 1.655401440E+02 & 1.655401440E+02 \\
      \hline
      Average $P$ & -9.378317550E+03 & -9.378317550E+03 \\
      Minimum $P$ & -4.155215280E+04 & -4.155215280E+04 \\
      Maximum $P$ & 2.058742010E+05 & 2.058742010E+05 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 500.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re500_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 6.479541170E-01 & 6.479541170E-01 \\
      Minimum $U$ & -2.550685400E+02 & -2.550685400E+02 \\
      Maximum $U$ & 6.663054900E+02 & 6.663054900E+02 \\
      \hline
      Average $V$ & 1.833690840E-01 & 1.833690840E-01 \\
      Minimum $V$ & -4.491052980E+02 & -4.491052980E+02 \\
      Maximum $V$ & 2.474376340E+02 & 2.474376340E+02 \\
      \hline
      Average $P$ & 1.833690840E-01 & 1.833690840E-01 \\
      Minimum $P$ & -6.241704500E+04 & -6.241704500E+04 \\
      Maximum $P$ & 3.518174810E+05 & 3.518174810E+05 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification for a Reynolds
      number of 700.} \textit{The values reported are global minima,
      maxima, and averages for each variable in the problem. The
      velocity is given in components in the $x$ and $y$ directions.}}
  \label{tab:driven_re700_results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\ 
      Minimum $P$ & \\ 
      Maximum $P$ & \\ 
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 200.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re200_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 300.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 400.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re400_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 500.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re500_results}
\end{table}
